Parallelization of Fast $\ell_1$-Minimization for Face Recognition

### 2011-04-17 main.tex
More mergning... need to print out...

To mitigate the problem, if the system can obtain to a good initial guess of the transformation $\tau$ (\eg, provided by a good face detector),
the optimal solution for $\tau$ can be sought iteratively by a sequence of linearized approximations $j=1, 2, \cdots$ as follows:
\begin{equation}
\min_{\xx, \ee, \Delta \tau_j}\|\ee\|_1\quad \subj\quad \tilde\bb\circ\tau_j +  J_j\Delta \tau_j = A_i\xx + \ee,
\end{equation}
If the warping $\tau$ is constrained to be a similarity transform,
it can be paramaterized in such a way that the computation of $\frac{\partial \bb}{\partial \tau_p}$
reduces to several linear vector operations involving pixel coordinates $(u,v)$, $\tau \in \Re^4$,
and the image gradients $\f_x, \f_y \in \Re^M$, the latter of which only has to be computed
once per test image.  The per-user iterative alignment algorithm is summarized as Algorithm \eqref{alg:iterative_alignment}.
\begin{algorithm}[thb]
\caption{\bf (Per-User Iterative Alignment)} \label{alg:iterative_alignment}
\begin{algorithmic}[1]
\begin{small}
\STATE {\bf Input:} Aligned training images $\{A_i \in \Re^{m\times n}\}$ for gallery subject $i$, the test image
$\f\in\Re^M$ 
%\STATE $\tau^{(0)} \leftarrow \textrm{face detector($\f$)}$. 
%\STATE $\f_x, \f_y \in \Re^M \leftarrow \frac{df}{dx}, \frac{df}{dy}$ 
%\STATE {\bf for} each gallery subject $i$, 
\STATE \hspace{0mm} {\bf while} not converged $(j=1,2,\ldots)$ {\bf do} 
\STATE \hspace{3mm} $\tilde \bb(\tau) \leftarrow \frac{\bb \circ \tau}{\|\bb \circ \tau\|_2}$;
\STATE \hspace{3mm} $J \leftarrow  \frac{\partial}{\partial \tau} \tilde\bb(\tau)  \bigr|_{\tau^{(j)}} $;
\STATE \hspace{3mm} $\Delta \tau =  \arg\min \; \| \e \|_1  \; \subj \; \tilde \bb + J \Delta \tau = A_i \x + \e.$ 
\STATE \hspace{3mm} $\tau^{(j+1)} \leftarrow \tau^{(j)} + \Delta
\tau$; 
\end{small}
\end{algorithmic}
\end{algorithm}

The solution of the minimization problem in Algorithm
\eqref{alg:iterative_alignment} Step 7 can be solved via a
variant of ALM, which is summarized as Algorithm \eqref{alg:alignment_alm}.
$\gamma$ denotes the largest eigenvalue of the matrix $A^TA$. For the choice of
parameter $\mu$, we take the same strategy as in \cite{YangJ2009-pp} and set
$\mu_0 = 2m / \|\bb\|_1$. We set $\rho=1.5$.

\begin{algorithm}[h]
\caption{\bf (Augmented Lagrange Multiplier Method For Alignment)}
\begin{algorithmic}[1]
\STATE {\bf Input:} $\bb \in \Re^m$, $A \in \Re^{m \times n}$,
$\x_1 = \mathbf{0}$, $\blamda_1 = \mathbf{0}$.
\WHILE{not converged ($k = 1,2,\ldots$)}
\STATE $t_{1} \leftarrow 1, z_{1} \leftarrow \x_{k}, \u_{1} \leftarrow \x_{k}$;
\WHILE{not converged ($l = 1,2,\ldots$)}
\STATE $\e_{l+1} \leftarrow \textup{shrink}\left(\bb - A\x_l + \frac{\blamda_k}{\mu_k}, \frac{1}{\mu_k}\right)$;
\STATE $\x_{l+1} \leftarrow (A^\dagger)^T \left(\bb - \e_{l+1} + \frac{\blamda_k}{\mu_k} \right) $;
\ENDWHILE
\STATE $\blamda_{k+1} \leftarrow \blamda_k + \mu (\bb - A\x_{k+1} - \e_{k+1})$;
\STATE $\mu_{k+1} \leftarrow \rho\mu_k$;
\ENDWHILE \STATE
{\bf Output:} $\x^* \leftarrow \x_k, \e^* \leftarrow \e_k$.
\end{algorithmic}
\label{alg:alignment_alm}
\end{algorithm}
%\STATE Compute residuals $r_i(\bb) = \| {\bb} - {A}_i \, \delta_i(\hat{\x}) \|_2$ for $i = k_1, \dots, k_S$.

\subsection{Computational Complexity and Parallelism} Any discussion of the speed of an
algorithm should discuss the comutational complexity of the algorithm.  For the
alignment stage ALM algorithm \eqref{alg:alignment_alm}, this is rather simple.
The Matrix-vector computions are $O(mn)$, and the vector-vector operations are
$O(m)$, in terms of both computation cost and memory-bandwidth.  Since A is
very tall, the computation of $A^\dagger$, the pseudoinverse of $A$, is best
computed via $A^\dagger = (A^TA)^{-1} A^T$.  The complexity of computing $G =
A^T A$ is $O(nnm)$.  $G$ is sufficiently small that it can be inverted via
Gauss-Jordan elimination, which has a complexity of $O(n^3)$.  The computation
of $A$ finishes with a matrix multiplication, with cost $O(n^2 m)$.
Fortunately, $A^\dagger$ only needs to be computed once per instance of the
$\ell_1$ minimization problem.

Therefore, for problems with large $n$, we expect the computation of the
pseudoinverse to dominate.  However, for the problem sizes needed in face
recognition problems, we find that the computation time is dominated by the
bandwidth required by repeated computation of matrix-vector and matrix-matrix
multiplications in the inner loop.

In summary, the alignment stage essentially two levels of available
parallelism: at the higher level there are multiple iterative alignent problems
that are solved independently, or {\bf problem-level} parallelism.  At a lower
level, the first-order linear algebraic operations exhibit parallelism within
image operations, i.e. at a pixel level.  We term this {\bf pixel-level}
parallelism.  In the following two sections will will discuss how to
exploit these two levels of parallelism on cpu and gpu architectures.

@@

\section{Parallelization of the Face Recognition Stage}
\label{sec:recognition}
{\bf AY: Add an algorithm here describe the recognition block in the pipeline. Explain the algorithm and necessary modification from generic l-1}
{\bf VS: Why did we modify the algorithm for the recognition stage? }

Below is the algorithm for the face recognition stage in Figure \ref{fig:pipeline}, which
solves the $\ell_1$ minimization problem posed in \eqref{eq:l1min_denoise}.

\begin{algorithm}[t]
\caption{\bf (Face Recognition via ALM)}
\begin{algorithmic}[1]
\begin{small}
\STATE {\bf Input:} $\bb \in \Re^m$, $A \in \Re^{m \times n}$,
$\x_1 = \mathbf{0}$, $\e_1 = \bb$, $\y_1 =
\mathbf{0}$.
\WHILE{not converged ($k = 1,2,\ldots$)}
\STATE $\e_{k+1} = \textup{shrink}\left(\bb - A\x_k +
\frac{1}{\mu}\y_k, \frac{1}{\mu}\right)$;
\STATE $t_1\leftarrow 1$, $\z_1 \leftarrow \x_k$, $\w_1 \leftarrow \x_k$;
\WHILE{not converged ($l = 1,2,\ldots$)}
\STATE $\w_{l+1} \leftarrow \textup{shrink}\left(\z_l +
\frac{1}{\gamma}A^T\left(\bb - A\z_l - \e_{k+1} +
\frac{1}{\mu}\y_k\right), \frac{1}{\mu\gamma}\right)$;
\STATE $t_{l+1} \leftarrow \frac{1}{2}\left( 1 +
\sqrt{1+4t_l^2}\right)$;
\STATE $\z_{l+1} \leftarrow \w_{l+1} + \frac{t_l - 1}{t_{l+1}}(\w_{l+1} - \w_l)$;
\ENDWHILE
\STATE $\x_{k+1} \leftarrow \w_{l}$,  \; $\y_{k+1} \leftarrow \y_k + \mu (\bb - A\x_{k+1} - \e_{k+1})$;
\ENDWHILE \STATE
{\bf Output:} $\x^* \leftarrow \x_k, \e^* \leftarrow \e_k$.
\end{small}
\end{algorithmic}
\label{alg:alm_rec} 
\end{algorithm}

@@

\section{Experiments}

In this section, we benchmark the performance of our parallel implementations
of $\ell_1$ minimization on CPU and GPU platforms.  In order to show how our
$\ell_1$ minimization algorithms scale with problem size, in Section
\ref{sec:simulation} we will begin with benchmarks on synthetic data.  We will
then progress in Sections \ref{sec:alignment_benchmark} and
\ref{sec:recognition_benchmark} to demonstrating the speed of our
implementations as applied to the alignment and recognition stages of the face
recognition problem.

To generate a meaningful comparison between different hardware architectures,
in all cases we compare the performance of hardware architectures on a
per-board basis:  For CPU implementations, the benchmark makes use of all of
the cores in as many cpu's are present.  For GPU implementations, the benchmark
makes the best use of the entire GPU chip (most GPU boards have a single GPU
chip).  Unless otherwise specified, all implementations utilize single
precision floating point datatypes.

@@

The first experiment compares the performance of our two proposed implementations of 
the general $\ell_1$-minimization problem (Algorithm \eqref{alg:alm}) given a generic random matrix $A$ and a random sparse
vector $\xx_0$.  
The measurement $d \times n$ matrix $A$ was generated as a random Gaussian matrix, with each entry
randomly generated from the standard normal and normalized with unit column norm.  The ratio of $d:n$ varied from
$1:10$ to $5:10$ with $n$ varying from 500 to 8000.
The ground truth signals, $\xx_0$ had a sparsity rate of 0.1 with elements generated using the standard normal and also normalized with unit norm.
Because the ground truth signal $\xx_0$ was known, the algorithm terminated
when $\|\bx-\bx_0\| < \tau$.
The measurement vector was generated with the equation $\bb_0 = A \xx_0$.

The results of this benchmark can be found in Figure \ref{fig:random_data}.
The x-axis represents the size of the $A$ matrix and the y-axis represents the
average amount of time it to complete a single problem instance.  The GPU implementation tends to be faster than
the CPU implementation at solving a single large problem, whereas the the CPU
implementation is faster at solving a single small problem.  Figure \ref{fig:random_data2} shows the various sizes and tolerances at which our GPU implementation
begins to run faster than the CPU implementation on synthetic data and will provide researchers 
with a starting point of where to begin setting their tolerance levels for the ALM algorithm.
\begin{figure}
\begin{center}
\includegraphics[width=3.5in]{results/random_data/time_vs_matrix_size_constant_tol}
\end{center}
\caption{Speed vs Dimensions of A.  Outer loop tolerance = 0.1.  Inner loop tolerance = $10^{-5}$}
\label{fig:random_data}
\end{figure}

>>>>

To mitigate the problem, if the system can obtain to a good initial guess of the transformation $\tau$ (\eg, provided by a good face detector),
the optimal solution for $\tau$ can be sought iteratively by a sequence of linearized approximations $j=1, 2, \cdots$ as follows:
\begin{equation}
\min_{\xx, \ee, \Delta \tau_j}\|\ee\|_1\quad \subj\quad \tilde\bb\circ\tau_j +  J_j\Delta \tau_j = A_i\xx + \ee,
\end{equation}
where $J_j = \nabla_{\tau_j}(\tilde\bb\circ\tau_j)$ is the Jacobian, and
$\Delta \tau$ is a step update to $\tau$. Denote $\bb_j =
\tilde\bb\circ\tau_j$, $B_j = [A_i, -J_j]$ and $\ww^T = [\xx^T, \Delta
\tau^T]$, then the update $\Delta \tau$ can be computed by solving the
following linear program:
\begin{equation}
\min_{\ww, \ee}\|\ee\|_1\quad \subj\quad \bb_j = B_j\ww + \ee.
\label{eq:alignment-linearization}
\end{equation}
%If the warping $\tau$ is constrained to be a similarity transform,
%it can be paramaterized in such a way that the computation of $\frac{\partial \bb}{\partial \tau_p}$
%reduces to several linear vector operations involving pixel coordinates $(u,v)$, $\tau \in \Re^4$,
%and the image gradients $\f_x, \f_y \in \Re^M$, the latter of which only has to be computed
%once per test image.

The per-class alignment algorithm via ALM is summarized in Algorithm
\ref{alg:alignment_alm}. In terms of computational complexity, one significant
term is the computation of the matrix psudo-inverse $B_j^\dagger$, whose
computational cost is bounded by $O(n_i^2m + n_i^3)$. For per-class face
alignment, since both $A_i$ and $J_{j}$ are very tall matrices (\ie, $m\gg n_i$
for all $i=1, \cdots, K$ classes), we find that the computation time is still
dominated by the iterative computation of matrix-vector multiplications in the
inner loop.
\begin{algorithm}[ht!]
\caption{\bf (Face Alignment via ALM)} \label{alg:alignment_alm}
{\bf Input:} $\bb$, $A_i$, $\x_0 = \mathbf{0}$, $\tau_0$, and $J_0$.
\begin{algorithmic}[1]
\WHILE{not converged ($j = 1,2,\ldots$)}
\STATE Update $\bb_j \leftarrow \frac{\bb\circ \tau_{j-1}}{\|\bb\circ \tau_{j-1}\|}$; $B_j= [A_i, -J_{j-1}]$ and corresponding $(B_j^\dagger)^T$
\STATE Initialize $\ww_0 = \mathbf 0$, $\yy_0 = \mathbf 0$
\WHILE{not converged ($k = 1,2,\ldots$)}
\STATE $\uu_0\leftarrow \ww_{k-1}$; $\zz_0\leftarrow \ee_{k-1}$
\WHILE{not converged ($l = 1,2,\ldots$)}
\STATE $\zz_l \leftarrow \mbox{shrink}\left(\bb_j - B_j\uu_{l-1} + \frac{\yy_{k}}{\mu_{k-1}}, \frac{1}{\mu_{k-1}}\right)$
\STATE $\uu_l \leftarrow (B_j^\dagger)^T \left(\bb_j - \zz_{l} + \frac{\yy_{k-1}}{\mu_{k-1}} \right) $
\ENDWHILE
\STATE $\ww_k \leftarrow \uu_l$; $\ee_k \leftarrow \zz_l$
\STATE $\yy_{k} \leftarrow \yy_{k-1} + \mu_{k-1} (\bb_j - B_j\ww_{k} - \e_{k})$
\STATE $\mu_{k} \leftarrow \rho\mu_{k-1}$
\ENDWHILE
\STATE Update $\ee_j$, $\tau_j$, and $J_j$
\ENDWHILE
\end{algorithmic}
{\bf Output:} $\tau^*\leftarrow \tau_j, \e^*\leftarrow \ee_j$
\end{algorithm}

In summary, the alignment stage essentially contains two levels of available
parallelism. At the higher level, there are per-class alignment problems
that are solved independently, or \emph{problem-level parallelism}.  At a lower
level, the first-order linear algebraic operations exhibit parallelism within
image operations, \ie, at the pixel level.  We call this \emph{pixel-level
parallelism}.  In the following two sections will will discuss how to
exploit these two levels of parallelism on different CPU and GPU architectures.

@@

\section{Parallelization of the Face Recognition Stage}
\label{sec:recognition}
After the face alignment stage is complete, a single recognition algorithm will
be called to estimate a sparse representation of the query image w.r.t. all the
training classes, as shown in \eqref{eq:l1min_denoise}. In
\cite{WrightJ2009-PAMI,YangA2010-ICIP,WagnerA2011-PAMI}, the recognition
algorithm via $\ell_1$-min has been extensively studied. The algorithm itself
via ALM is summarized in Algorithm \ref{alg:alm_rec}.  In this section, we
mainly focus our discussion on its pixel-level parallelism on the multicore
CPUs and GPUs. Then in Section \ref{sec:experiment}, we benchmark the
performance of the two architectures and further demonstrate the improvement in
both accuracy and speed compared to the existing literature.
\begin{algorithm}[t]
\caption{\bf (Face Recognition via ALM)} \label{alg:alm_rec} 
\begin{algorithmic}[1]
\begin{small}
\STATE {\bf Input:} $\bb \in \Re^m$, $A \in \Re^{m \times n}$,
$\x_1 = \mathbf{0}$, $\e_1 = \bb$, $\y_1 =
\mathbf{0}$.
\WHILE{not converged ($k = 1,2,\ldots$)}
\STATE $\e_{k+1} = \textup{shrink}(\bb - A\x_k +
\frac{1}{\mu}\y_k, \frac{1}{\mu})$;
\STATE $t_1\leftarrow 1$, $\z_1 \leftarrow \x_k$, $\w_1 \leftarrow \x_k$;
\WHILE{not converged ($l = 1,2,\ldots$)}
\STATE $\w_{l+1} \leftarrow \textup{shrink}(\z_l +
\frac{1}{\gamma}A^T(\bb - A\z_l - \e_{k+1} +
\frac{1}{\mu}\y_k), \frac{1}{\mu\gamma})$;
\STATE $t_{l+1} \leftarrow \frac{1}{2}( 1 +
\sqrt{1+4t_l^2})$;
\STATE $\z_{l+1} \leftarrow \w_{l+1} + \frac{t_l - 1}{t_{l+1}}(\w_{l+1} - \w_l)$;
\ENDWHILE
\STATE $\x_{k+1} \leftarrow \w_{l}$,  \; $\y_{k+1} \leftarrow \y_k + \mu (\bb - A\x_{k+1} - \e_{k+1})$;
\ENDWHILE \STATE
{\bf Output:} $\x^* \leftarrow \x_k, \e^* \leftarrow \e_k$.
\end{small}
\end{algorithmic}
\end{algorithm}

@@

\section{Experiments}
\label{sec:experiment}
In this section, we benchmark the performance of our parallel implementations
of $\ell_1$ minimization on CPU and GPU platforms.  In order to show how our
$\ell_1$ minimization algorithms scale with problem size, in Section
\ref{sec:simulation} we will begin with benchmarks on synthetic data.  We will
then progress in Sections \ref{sec:alignment_benchmark} and
\ref{sec:recognition_benchmark} to demonstrating the speed of our
implementations as applied to the alignment and recognition stages of the face
recognition problem.

To generate a meaningful comparison between different hardware architectures,
in all cases we compare the performance of hardware architectures on a
per-board basis:  For CPU implementations, the benchmark makes use of all of
the cores in as many cpu's are present.  For GPU implementations, the benchmark
makes the best use of the entire GPU chip (most GPU boards have a single GPU
chip).  Unless otherwise specified, all implementations utilize single-precision 
floating point datatypes.

@@

The first experiment compares the performance of our two proposed
implementations of the general $\ell_1$-min (Algorithm \eqref{alg:alm}) given a
generic random matrix $A$ and a random sparse vector $\xx_0$.  The measurement
$d \times n$ matrix $A$ was generated as a random Gaussian matrix, with each
entry randomly generated from the standard normal and normalized with unit
column norm.  The ratio of $d:n$ varied from $1:10$ to $5:10$ with $n$ varying
from 500 to 8000.  The ground truth signals, $\xx_0$ had a sparsity rate of 0.1
with elements generated using the standard normal and also normalized with unit
norm.  Because the ground truth signal $\xx_0$ was known, the algorithm
terminated when $\|\bx-\bx_0\| < \tau$.  The measurement vector was generated
with the equation $\bb_0 = A \xx_0$.

The results of this benchmark can be found in Figure \ref{fig:random_data}.
The x-axis represents the size of the $A$ matrix and the y-axis represents the
average amount of time it to complete a single problem instance.  The GPU
implementation tends to be faster than the CPU implementation at solving a
single large problem, whereas the the CPU implementation is faster at solving a
single small problem.  Figure \ref{fig:random_data2} shows the various sizes
and tolerances at which our GPU implementation begins to run faster than the
CPU implementation on synthetic data and will provide researchers with a
starting point of where to begin setting their tolerance levels for the ALM
algorithm.
\begin{figure}
\begin{center}
\includegraphics[width=3.5in]{results/random_data/time_vs_matrix_size_constant_tol}
\end{center}
\caption{Speed vs Dimensions of $A$.}
\label{fig:random_data}
\end{figure}

### 2011-04-17 main_allen.tex
More mergning... need to print out...

To mitigate the problem, if the system can obtain to a good initial guess of the transformation $\tau$ (\eg, provided by a good face detector),
the optimal solution for $\tau$ can be sought iteratively by a sequence of linearized approximations $j=1, 2, \cdots$ as follows:
\begin{equation}
\min_{\xx, \ee, \Delta \tau_j}\|\ee\|_1\quad \subj\quad \tilde\bb\circ\tau_j +  J_j\Delta \tau_j = A_i\xx + \ee,
\end{equation}
where $J_j = \nabla_{\tau_j}(\tilde\bb\circ\tau_j)$ is the Jacobian, and $\Delta \tau$ is a step update to $\tau$. Denote $\bb_j = \tilde\bb\circ\tau_j$, $B_j = [A_i, -J_j]$ and $\ww^T = [\xx^T, \Delta \tau^T]$, then the update $\Delta \tau$ can be computed by solving the following linear program:
\begin{equation}
\min_{\ww, \ee}\|\ee\|_1\quad \subj\quad \bb_j = B_j\ww + \ee.
\label{eq:alignment-linearization}
\end{equation}

@@

For CPU implementation, {\bf AY: Drew, please fill in one or two paragraphs}.

For GPU implementation, {\bf AY: Drew, please fill in one or two paragraphs}.

\section{Experiment}
\label{sec:experiment}
In this section, we benchmark the performance of our parallel implementations
of $\ell_1$ minimization on CPU and GPU platforms.  In order to show how our
$\ell_1$ minimization algorithms scale with problem size, in Section
\ref{sec:simulation} we will begin with benchmarks on synthetic data.  We will
then progress in Sections \ref{sec:alignment_benchmark} and
\ref{sec:recognition_benchmark} to demonstrating the speed of our
implementations as applied to the alignment and recognition stages of the face
recognition problem.

>>>>

To mitigate the problem, if the system can obtain to a good initial guess of the transformation $\tau$ (\eg, provided by a good face detector),
the optimal solution for $\tau$ can be sought iteratively by a sequence of linearized approximations $j=1, 2, \cdots$ as follows:
\begin{equation}
\min_{\xx, \ee, \Delta \tau_j}\|\ee\|_1\quad \subj\quad \tilde\bb\circ\tau_j +  J_j\Delta \tau_j = A_i\xx + \ee,
\end{equation}
where $J_j = \nabla_{\tau_j}(\tilde\bb\circ\tau_j)$ is the Jacobian, and
$\Delta \tau$ is a step update to $\tau$. Denote $\bb_j =
\tilde\bb\circ\tau_j$, $B_j = [A_i, -J_j]$ and $\ww^T = [\xx^T, \Delta
\tau^T]$, then the update $\Delta \tau$ can be computed by solving the
following linear program:
\begin{equation}
\min_{\ww, \ee}\|\ee\|_1\quad \subj\quad \bb_j = B_j\ww + \ee.
\label{eq:alignment-linearization}
\end{equation}
%If the warping $\tau$ is constrained to be a similarity transform,
%it can be paramaterized in such a way that the computation of $\frac{\partial \bb}{\partial \tau_p}$
%reduces to several linear vector operations involving pixel coordinates $(u,v)$, $\tau \in \Re^4$,
%and the image gradients $\f_x, \f_y \in \Re^M$, the latter of which only has to be computed
%once per test image.

@@

\subsection{CPU Implementation} Our CPU implementation of Algorithm
\ref{alg:alm_rec} was written in C++.  For operations in the algorithm that map
nicely onto the BLAS API (such as SGEMV, SAXPY), we
call Intel's MKL BLAS library, which internally takes advantage of the SSE
units on all available CPU cores.

For operations that do not map nicely onto the BLAS API, such as the shrinkage
operator, {\bf Argue that these parts are optimized, and/or demonstrate that
performance of these parts is insignificant}.

\subsection{GPU Implementation} Our GPU implementation of Algorithm
\ref{alg:alm_rec} is similar to the CPU implementation described in the
previous section, in that only one problem is solved at a time, and each linear
algebraic operation is parallelized separately.

For most of the operations, calls to MKL CPU BLAS library map directly onto
similar calls in Nvidia's GPU BLAS library (CUBLAS).  The CUBLAS library is
designed to utilize all of the SM's on the GPU.

Operations that do not map well onto the BLAS API (mostly combined
vector-vector operations) were implemented as gpu kernels (in C for CUDA).
Even for operations that could have been implemented via multiple BLAS calls,
this was found to have better performance due to reduced bandwidth and kernel
call overhead {\bf Victor, verify or correct this.  I'm not sure, currently asking Mark}.

In order to avoid expensive data transfer across the bus connecting the GPU
card and the CPU motherboard (the PCI express bus), all of the data is
transferred to GPU DRAM once, and all non-trivial tasks are performed on the
GPU on data stored in GPU DRAM.  The sole exception to the above implementation
strategy is that the pseudoinverse of A is still computed on the CPU via the
LAPACK implementation that is part of Intel's MKL. This operation need only be
performed (and results uploaded to GPU DRAM) once before GPU computation
starts. {\bf we should prove justification for A pseudoinverse being cheap,
either here or perhaps later in a pie chart}

\section{Experiments}
\label{sec:experiment}
In this section, we benchmark the performance of our parallel implementations
of $\ell_1$ minimization on CPU and GPU platforms.  In order to show how our
$\ell_1$ minimization algorithms scale with problem size, in Section
\ref{sec:simulation} we will begin with benchmarks on synthetic data.  We will
then progress in Sections \ref{sec:alignment_benchmark} and
\ref{sec:recognition_benchmark} to demonstrating the speed of our
implementations as applied to the alignment and recognition stages of the face
recognition problem.
